Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-13 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 While the Global Moran's I could be used with great success to identify spatial association in smaller areas affected by the virus and and help in decision making while dealing with local outbreaks, the *LISA* would be useful not only to identify with more precision where the spatial association is occurring but it also should be used when the goal is to control Covid-19 outbreaks in larger areas. The Spatio-Temporal Scan Statistic should be used when trying to identify "alive" *clusters* and when they started, therefore it would be a great tool in decision making when dealing not only with Covid-19 but with other disease outbreaks.

>>>>

 While the Global Moran's I could be used with great success to identify spatial association in smaller areas affected by the virus and help in decision making while dealing with local outbreaks, the *LISA* would be useful not only to identify with more precision where the spatial association is occurring but it also should be used when the goal is to control Covid-19 outbreaks in larger areas. The Spatio-Temporal Scan Statistic should be used when trying to identify "alive" *clusters* and their initial date, therefore it would be a great tool in decision making when dealing not only with Covid-19 but with other disease outbreaks.
